raptr: Representative and Adequate Prioritisation Toolkit in R

### 2016-08-17 code/rmarkdown/article.Rmd
+ use checkpoint in rmd files

```{r, include=FALSE}
## initialization
# load .rda file
try(session::restore.session('data/final/results.rda'))

>>>>

```{r, include=FALSE}
## initialization
# load .rda file
checkpoint::checkpoint('2016-07-25', R.version='3.3.1', scanForPackages=FALSE)
try(session::restore.session('data/final/results.rda'))
